Figures for "Sources and consequences of mismatch between leaf disc and whole-leaf leaf mass per area (LMA)

### 2022-05-03 report.Rmd
add tab

```{r, eval=TRUE}
tar_load(sma_sp_tab)
sma_sp_tab |>
  kable() |>
  kable_styling()
```

@@

@@

>>>>

```{r, eval=TRUE}
tar_load(sma_sp_tab)
sma_sp_tab |>
  kable() |>
  kable_styling()
```
```{r}
sma_sp_tab |>
  write_csv("data/sma_sp_tab.csv")
```

@@

```{r}
sma_sp_ld_tab |>
  write_csv("data/sma_sp_ld_tab.csv")
```

@@

```{r}
sma_sp_2_tab |>
  write_csv("data/sma_sp_2_tab.csv")
```
